Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-05 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Edited Table 1 + Included the modified Figure 3

\begin{table}[]

@@

\caption{Simulated single component fully hydrated lipid bilayer systems. The simulation file data sets marked with $^*$ also include a part of the trajectory.
  If simulation data from previously published work has been directly used, the original publication is cited for simulation details. For other systems the simulation details
  are given in the Supplementary Information. The abbreviations are 1-palmitoyl-2-oleoylphosphatidylcholine (POPC), dipalmitoylphosphatidylcholine (DPPC), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),
1,2-dioleoyl-sn-glycero-3-phosphocholine (DOPC) and dilauroylphosphatidylcholine (DLPC).
$^a$ The number of lipid molecules
$^b$ The number of water molecules
$^c$ Simulation temperature
$^d$ The total simulation time
$^e$ Time frames used in the analysis
$^f$ Reference link for the downloadable simulation files
$^g$ Reference for the full simulation details

@@

\begin{tabular}{c c c c c c c c c}

@@

Force field & lipid  & $^a$N$_{\rm l}$   &  $^b$N$_{\rm w}$ &  $^c$T (K)  &  $^d$t$_{{\rm sim}}$(ns) &  $^e$t$_{{\rm anal}}$ (ns) &  $^f$Files  &  $^g$Details\\

@@

Berger-POPC-07~\cite{ollila07a}          &   POPC & 128 & 7290  & 298  & 270 & 240 & [\citenum{bergerFILESpopc}]$^*$ & [\citenum{ferreira15}] \\

@@

@@

CHARMM36~\cite{klauda10}      & POPC   & 128 &  5120    & 303 & 150 & 100  & [\citenum{charmm36files}]$^*$   & SI \\

@@

GAFFlipid~\cite{dickson12}       & POPC & 126  & 3948  & 303 & 137 & 32  & [\citenum{GAFFlipidFILES}]$^*$ & SI \\

@@

@@

\end{table}

@@

The most detailed experimentally available order parameter information for the glycerol backbone and choline 
segments of POPC bilayer is collected by taking the absolute values from~\cite{ferreira13}, the signs from~\cite{hong95a,hong95b,gross97} 
and the stereospecific labeling from~\cite{gally81}, and shown in Fig.~\ref{HGorderparameters2}.
\begin{figure*}[]
  \centering
  \includegraphics[width=8.6cm]{../Fig/HGorderparameters5.pdf} \\
  \todo{This figure should be updated similar to Fig.~\ref{HGorderparameters}} \\
  \caption{\label{HGorderparameters2}
  Order parameteres from simulations with Berger-POPC-07, CHARMM36, GAFFlipid and MacRog force fields together with experimental values for POPC glycerol and choline groups.
  The magnitudes for experimental order parameters are taken from Ferreira et al.~\cite{ferreira13}, the signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
  and Gross et al.~\cite{gross97}, and the R/S labeling is based in the measurements by Gally et al.~\cite{gally81}.
} 
\end{figure*}

>>>>

\begin{sidewaystable}[]

@@

\caption{Fully hydrated single component lipid bilayer systems simulated for Fig.~\ref{HGorderparameters}:
  1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC),
  %1,2-dioleoyl-sn-glycero-3-phosphocholine (DOPC),
  dilauroylphosphatidylcholine (DLPC),
  dipalmitoylphosphatidylcholine (DPPC), and
  1-palmitoyl-2-oleoylphosphatidylcholine (POPC).
The {\bf bolded} systems were used also for Fig.~\ref{HGorderparameters2}.
$^a$ Number of lipid molecules.
$^b$ Number of water molecules.
$^c$ Temperature.
$^d$ Total simulation time.
$^e$ Time used for analysis.
$^f$ Reference link for the downloadable simulation files;
     the data sets marked with $^*$ also include a part of the trajectory.
$^g$ Reference for the full simulation details;
     the original publication is cited if simulation data from previously published work has been directly used,
     for other systems the simulation details are given in the Supplementary Information.

@@

\begin{tabular}{l l r r r r r c c c}

@@

Force field & lipid & $^a$N$_{\rm l}$   &  $^b$N$_{\rm w}$ &  $^c$T (K)  &  $^d$t$_{{\rm sim}}$(ns) &  $^e$t$_{{\rm anal}}$ (ns) &  $^f$Files  &  $^g$Details & Notes\\

@@

{\bf
Berger-POPC-07}~\cite{ollila07a}   & POPC & 128 & 7290 & 298 & 270 & 240 & [\citenum{bergerFILESpopc}]$^*$ & [\citenum{ferreira15}] \\

@@

CHARMM36~\cite{klauda10}  & DPPC &  72 & 2189 & 323 &  ? &  130? & [?]$^*$    & ? & Magnitudes from Fig.~S4 of Klauda et al.~\cite{klauda10}, signs matched to our simulations. \\

@@

{\bf
CHARMM36}~\cite{klauda10} & POPC & 128 & 5120 & 303 & 200 & 100 & [\citenum{charmm36files}]$^*$      & SI \\

@@

{\bf
MacRog}~\cite{maciejewski14} & POPC & 128 &  6400 & 310 & 400 & 200 & [\citenum{macrogCHOLfiles}]$^*$  & SI  \\
MacRog~\cite{maciejewski14}  & POPC & 288 & 14400 & 310 &  90 &  40 & [\citenum{macrogdehydFILES}]$^*$ & SI  \\

@@

GAFFlipid~\cite{dickson12}   & DPPC &  ? & ? & 323 & ? &  250? & [?]$^*$    & ? & Magnitudes from Fig.~9 of Dickson et al.~\cite{dickson12}, signs matched to our simulations. \\
{\bf
GAFFlipid}~\cite{dickson12}  & POPC & 126 & 3948 & 303 & 137 & 32 & [\citenum{GAFFlipidFILES}]$^*$ & SI \\

@@

\end{sidewaystable}

@@

The most detailed experimentally available order parameter information for the glycerol backbone and choline 
segments of POPC bilayer is collected by taking the absolute values from~\cite{ferreira13}, the signs from~\cite{hong95a,hong95b,gross97} 
and the stereospecific labeling from~\cite{gally81}, and shown in Fig.~\ref{HGorderparameters2}.
\begin{figure*}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/stereospecificOPs.pdf} \\
  \todo{This figure should be updated similar to Fig.~\ref{HGorderparameters}. DONE.} \\
  \caption{\label{HGorderparameters2}
  Order parameteres for POPC glycerol and choline groups
  from simulations with Berger-POPC-07, MacRog, GAFFlipid, and CHARMM36 force fields
  (the {\bf bolded} systems in Table~\ref{systems})
  together with experimental values.
  The error bars of simulation data are standard errors of mean (see Methods for details).
  The magnitudes for experimental order parameters are taken from Ferreira et al.~\cite{ferreira13},
  the signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
  and Gross et al.~\cite{gross97}, and the R/S labeling is based on the measurements by Gally et al.~\cite{gally81}.
}
\end{figure*}
